Incentivizing Exploration by Heterogeneous Users

### 2018-06-05 problem_setting.tex
mostly accepted Peter's edits

We consider a multi-armed bandit setting with \ARMNUM arms.
Arm payoffs are determined by $d$ \emph{attributes} or \emph{features};
hence, arms are identified with vectors $\ArmV{i} \in \R^d$.
The \ArmV{i} are (adversarially) fixed, and unknown to the agents
and the principal.
When arm $i$ is pulled, its current utility-relevant features are
determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero independent Gaussian%
\footnote{For simplicity of notation, we assume that the variance
  $\sigma^2$ is uniform across time steps.
In fact, the analysis extends straightforwardly to any
continuous mean-zero sub-Gaussian($\sigma^2$) noise that is
independent but not necessarily identically distributed across time.
\dkcomment{Are we actually stating the result in this generality now?
  If not, then why make the algorithm use continuity, as opposed to
  that we have Gaussians? If we do make the algorithm that general,
  then we should just define everything for Gaussians here.}}
noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.
Here, $I_d$ denotes the $d \times d$ identity matrix.

>>>>

We consider a multi-armed bandit setting with \ARMNUM arms.
Arm payoffs are determined by $d$ \emph{attributes} or \emph{features};
hence, arms are identified with vectors $\ArmV{i} \in \R^d$.
The \ArmV{i} are (adversarially) fixed, and unknown to the agents
and the principal.
When arm $i$ is pulled, its current utility-relevant features are
determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero independent Gaussian%
\footnote{For simplicity of notation, we assume that the variance
  $\sigma^2$ is uniform across time steps.
In fact, the analysis extends straightforwardly to any
continuous mean-zero sub-Gaussian($\sigma^2$) noise that is
independent but not necessarily identically distributed across time.
\dkcomment{Are we actually stating the result in this generality now?
  If not, then why make the algorithm use continuity, as opposed to
  that we have Gaussians? If we do make the algorithm that general,
  then we should just define everything generally here.}}
noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.
Here, $I_d$ denotes the $d \times d$ identity matrix.
